### 2024-09-27 Manuscript/supplementaries.tex
Update supplementaries.tex

>>>>

\subsection{Glossary}

\begin{table}[ht]
\caption{Glossary and equivalence of terms used in this papers; adapted from \cite{guillerme2020shifting} and \cite{mammola2021concepts}.}
\centering
\begin{tabular}{p{4cm}p{5cm}p{5cm}p{3cm}}
This paper & Ecology & Macroevolution & Definition \\
\hline
Trait space & Functional space, morphospace , etc. & Morphospace, traitspace, etc. & Matrix ($n \times d$) with a structural relation between rows and columns  \\
\hline
Observations & Taxa, field sites, environments, etc. & Taxa, specimen, populations, elements, OTUs etc. & Rows ($n$) \\
\hline
Dimensions & Traits, Ordination scores, distances, etc. & Traits, ordination scores, distances, etc. & Columns ($d$) \\
\hline
Traits & uni/multidimensional trait; e.g. geographical location & uni/multidimensional trait; e.g. landmark coordinates & Columns subset ($b \times n$; $b \leq d$) \\
\hline
Group & Treatments, phylogenetic group (clade), etc. & Clades, geological stratum, etc. & Rows subset ($m \times d$; $m \leq n$) \\
\hline
Metric  & Dissimilarity index or metric, hypervolume, functional diversity, etc. & Disparity metric or index & Statistic (i.e. a measure) \\
\hline
Stressor & Introduction of invasive species, change of landscape use, climate change, polution, experimental design, etc. & Mass extinction, Tectonic change, climate change, etc. & An algorithm selecting a proportion of the observations.
\end{tabular}
\end{table}
